### 2025-06-04 README.Rmd

[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/R-CMD-check.yaml)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://app.codecov.io/github/tidymodels/infer/?branch=main)

>>>>

[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/R-CMD-check.yaml)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
[![Codecov test coverage](https://codecov.io/gh/tidymodels/infer/graph/badge.svg)](https://app.codecov.io/gh/tidymodels/infer)
